---
title: "Math Camp Computational Bootcamp: R Markdown"
author: "Henry Watson"
date: "8/19/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd()
world <- read.csv("poliscidata_world.csv")
```

# Introduction

For this R Workshop, we're going to walk through an exercise, writing up the results using "R Markdown". Markdown is a powerful tool for coding and writing in the same document. You don't *have* to use it for any of the assignments in this class, but it may actually make your life easier!

Some basics:

* To avoid worrying about setting working directories, place your data within the same folder as your Markdown file
* When you're just typing in the white space, that will be recorded as text, not code!
* You can use symbols to format your document! 
    + At the start, I used a # symbol at the start of a new line to indicate a header. Multiple #s will produce subheadings. 
    + I'm using * and + (with two indents) symbols at the start of each line in this section to produce a bulleted list.
    + In the first intro paragraph, I used asterisks around a word to *italicize* it. You can also use multiple asterisks to **bold**.
* To finish your document, use the "Knit" tool at the top of your window. This will save a pdf to the same folder in which you saved this R Markdown script.
* Refer to https://rmarkdown.rstudio.com/authoring_basics.html

# Coding

In Markdown, you'll probably want to run some code. Let's use the "Insert" -> "R" button at the top of the window to display a simple command.

```{r}
1 + 1
```

You can also hide the command and/or the results if you just want to run things without displaying the output.

```{r, echo=FALSE, results='hide'}
1 + 1
```

Let's run some of the code from Wednesday

```{r}
world_women <- subset(world, dem_level4 != "Authoritarian", select = c(country, dem_level4, women05, women09, women13))
# These variables record the percent women in the lower house of the legislature for democracies
# We can reshape this dataframe to make "year" a column variable
world_women_reshape <- reshape(world_women,
                               varying = c("women05", "women09", "women13"),
                               v.names = c("dem_level4"),
                               timevar = "year",
                               idvar = "country",
                               times = c(2005, 2009, 2013),
                               direction = "long")
```

We can display plots in a Markdown document (you might want to hide the code here using echo = FALSE)

```{r, echo = FALSE}
barplot(prop.table(table(world$dem_level4)))
```

We can add some labels to our plots as well

```{r, echo = FALSE}
barplot(prop.table(table(world$dem_level4)),
        names = c("Authoritarian", "Full Democracy", "Hybrid", "Partial Democracy"),
        xlab  = "Regime Type",
        ylab  = "Proportion of Countries",
        main  = "World Democracies")
```

